---
title: "Teaching Evaluations"
---

## Evaluation Trends Over Time

```{r}
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(dplyr)

# Load evaluation data from RDS file
# The RDS file should be generated by running: Rscript data/build_evals_data.R
rds_path <- "data/evals_data.rds"
if (!file.exists(rds_path)) {
  stop(
    "Evaluation data file not found at: ", rds_path, "\n",
    "Please run the build script to generate it:\n",
    "  ./build.sh\n",
    "Or generate it manually:\n",
    "  Rscript data/build_evals_data.R"
  )
}
evals <- readRDS(rds_path)

# Convert year to factor for proper ordering
evals$year <- as.factor(evals$year)

# Create a plot of overall ratings over time
ggplot(evals, aes(x = year, y = overall_rating, group = 1)) +
  geom_line(color = "#2780E3", linewidth = 1.2) +
  geom_point(color = "#2780E3", size = 3) +
  coord_cartesian(ylim = c(4.0, 5.0)) +
  labs(
    title = "Overall Teaching Rating Over Time",
    x = "Year",
    y = "Overall Rating (out of 5)",
    caption = "Data from UC Davis and UCLA teaching evaluations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10)
  )
```

The plots below are generated from evaluation data extracted from the linked PDF summaries. UCLA's 9-point teaching assistant scores are linearly rescaled to the 5-point UC Davis scale so they can be shown on the same axis.

```{r}
#| echo: false
#| message: false
#| warning: false

# Create a plot comparing different metrics
evals_long <- evals %>%
  select(year, overall_rating, instructor_effectiveness, course_organization) %>%
  tidyr::pivot_longer(
    cols = c(overall_rating, instructor_effectiveness, course_organization),
    names_to = "metric",
    values_to = "rating"
  )

# Clean up metric names for display
evals_long$metric <- factor(
  evals_long$metric,
  levels = c("overall_rating", "instructor_effectiveness", "course_organization"),
  labels = c("Overall Rating", "Instructor Effectiveness", "Course Organization")
)

ggplot(evals_long, aes(x = year, y = rating, color = metric, group = metric)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  coord_cartesian(ylim = c(3.5, 5.0)) +
  labs(
    title = "Teaching Evaluation Metrics Over Time",
    x = "Year",
    y = "Rating (out of 5)",
    color = "Metric",
    caption = "Data from UC Davis and UCLA teaching evaluations"
  ) +
  scale_color_manual(values = c("#2780E3", "#28A745", "#FFC107")) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.position = "bottom"
  )
```

## UC Davis (Instructor of Record)

### Epi 204

#### 2025

- [Epi 204 Evaluations Summary (2025)](files/evals/evals%20epi%20204%202025%20summary.pdf)

#### 2024

- [Epi 204 Evaluations Summary (2024)](files/evals/Evaluations%20epi%20204%202024%20summary.pdf)

#### 2023

- [Epi 204 Evaluations (Spring 2023)](files/evals/Epi%20204%20Evaluations%20Spring%202023.pdf)

## UCLA (Teaching Assistant)

### Winter 2017

- [Teaching Evaluation 1](files/evals/Morrison%20teaching%20eval%201.pdf)
- [Teaching Evaluation 2](files/evals/Morrison%20teaching%20eval%202.pdf)
