---
title: "Teaching Evaluations"
---

## Evaluation Trends Over Time

```{r}
#| label: setup-evals
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(dplyr)
library(tidyr)

rds_path <- "data/evals_data.rds"
if (!file.exists(rds_path)) {
  stop(
    "Evaluation data file not found at: ", rds_path, "\n",
    "Please run the build script to generate it:\n",
    "  ./build.sh\n",
    "Or generate it manually:\n",
    "  Rscript data/build_evals_data.R"
  )
}
evals <- readRDS(rds_path)

evals$role <- ifelse(
  grepl("TA", evals$course, fixed = TRUE),
  "UCLA (TA)",
  "UC Davis (Instructor of Record)"
)

year_breaks <- sort(unique(evals$year))
role_colors <- c("UC Davis (Instructor of Record)" = "#2780E3",
                 "UCLA (TA)" = "#E67E22")

rating_plot <- function(metric, ymin_break = 1) {
  sd_col <- paste0(metric, "_sd")
  df <- data.frame(
    year   = evals$year,
    role   = evals$role,
    rating = evals[[metric]],
    sd     = evals[[sd_col]],
    n      = evals$n_responses
  )

  ggplot(df, aes(x = year, y = rating, color = role, shape = role)) +
    geom_errorbar(
      aes(ymin = pmax(rating - sd, 1), ymax = pmin(rating + sd, 5)),
      width = 0.4, linewidth = 0.5, alpha = 0.6
    ) +
    geom_line(aes(group = role), linewidth = 0.8) +
    geom_point(aes(size = n)) +
    geom_text(aes(label = paste0("n=", n)),
              vjust = -1.4, hjust = 0.5, size = 3, show.legend = FALSE) +
    scale_x_continuous(breaks = year_breaks) +
    scale_y_continuous(limits = c(1, 5), breaks = ymin_break:5) +
    scale_size_continuous(range = c(2.5, 5), name = "Respondents",
                          guide = guide_legend(order = 2)) +
    scale_color_manual(values = role_colors, name = "Role",
                       guide = guide_legend(order = 1)) +
    scale_shape_discrete(name = "Role", guide = guide_legend(order = 1)) +
    labs(x = "Year", y = "Mean rating") +
    theme_minimal() +
    theme(legend.position = "bottom", legend.box = "vertical")
}

response_rate_plot <- function() {
  ggplot(evals, aes(x = year, y = response_rate, color = role, shape = role)) +
    geom_line(aes(group = role), linewidth = 0.8) +
    geom_point(aes(size = n_responses)) +
    geom_text(aes(label = paste0("n=", n_responses)),
              vjust = -1.4, hjust = 0.5, size = 3, show.legend = FALSE) +
    scale_x_continuous(breaks = year_breaks) +
    scale_y_continuous(labels = scales::percent, limits = c(0, 1),
                       breaks = seq(0, 1, 0.25)) +
    scale_size_continuous(range = c(2.5, 5), name = "Respondents",
                          guide = guide_legend(order = 2)) +
    scale_color_manual(values = role_colors, name = "Role",
                       guide = guide_legend(order = 1)) +
    scale_shape_discrete(name = "Role", guide = guide_legend(order = 1)) +
    labs(x = "Year", y = "Response rate") +
    theme_minimal() +
    theme(legend.position = "bottom", legend.box = "vertical")
}
```

::: {#fig-evals layout-ncol=1}

```{r}
#| label: fig-overall
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Overall rating (UC Davis Likert anchors: 1 = Poor, 5 = Excellent)."
rating_plot("overall_rating")
```

```{r}
#| label: fig-instructor
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Instructor effectiveness (UC Davis Likert anchors: 1 = Poor, 5 = Excellent)."
rating_plot("instructor_effectiveness")
```

```{r}
#| label: fig-organization
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Course was well-organized (UC Davis Likert anchors: 1 = Strongly Disagree, 5 = Strongly Agree)."
rating_plot("course_organization")
```

```{r}
#| label: fig-response-rate
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Response rate (respondents ÷ enrolled). No error bars — this is a population proportion, not a sample mean."
response_rate_plot()
```

Teaching-evaluation trends over time. In the three rating panels, points show the mean rating and error bars span **±1 standard deviation** of the individual respondent ratings (a measure of student-to-student spread, *not* the standard error of the mean), clipped to the [1, 5] scale. Point size is proportional to the number of respondents (also labeled `n=...`). The three rating items use different Likert anchors and aren't directly comparable across panels. UCLA TA evaluations used a 9-point scale (1 = Very Low … 9 = Very High); both means and SDs are linearly rescaled to the 5-point UC Davis scale.

:::

## UC Davis (Instructor of Record)

### Epi 204

#### 2025

- [Epi 204 Evaluations Summary (2025)](files/evals/evals%20epi%20204%202025%20summary.pdf)

#### 2024

- [Epi 204 Evaluations Summary (2024)](files/evals/Evaluations%20epi%20204%202024%20summary.pdf)

#### 2023

- [Epi 204 Evaluations (Spring 2023)](files/evals/Epi%20204%20Evaluations%20Spring%202023.pdf)

## UCLA (Teaching Assistant)

### Winter 2017

- [Teaching Evaluation 1](files/evals/Morrison%20teaching%20eval%201.pdf)
- [Teaching Evaluation 2](files/evals/Morrison%20teaching%20eval%202.pdf)
