---
title: "Teaching Evaluations"
---

## Evaluation Trends Over Time

```{r}
#| label: setup-evals
#| echo: false
#| message: false
#| warning: false

library(ggplot2)
library(dplyr)
library(tidyr)

rds_path <- "data/evals_data.rds"
if (!file.exists(rds_path)) {
  stop(
    "Evaluation data file not found at: ", rds_path, "\n",
    "Please run the build script to generate it:\n",
    "  ./build.sh\n",
    "Or generate it manually:\n",
    "  Rscript data/build_evals_data.R"
  )
}
evals_data <- readRDS(rds_path)
evals      <- evals_data$summary
responses  <- evals_data$responses

# Lift every rating onto the UCLA 9-point axis: 9pt = 1 + (5pt - 1) * 2.
# Means and SDs were already converted earlier; do the same for the raw
# UC Davis responses so violins and the summary line live in the same space.
responses$rating_9 <- ifelse(
  responses$scale_max == 5,
  1 + (responses$rating - 1) * 2,
  responses$rating
)
responses <- merge(responses,
                   evals[, c("year", "role", "response_rate", "n_responses")],
                   by = c("year", "role"))

year_breaks <- sort(unique(evals$year))
role_colors <- c("UC Davis (Instructor of Record)" = "#2780E3",
                 "UCLA (TA)" = "#E67E22")

# Plot all ratings on the UCLA 9-point scale (left axis). Data stored as
# 5-point gets stretched: nine_pt = 1 + (five_pt - 1) * 2; SDs scale by 2.
five_to_nine     <- function(x) 1 + (x - 1) * 2
nine_to_five     <- function(x) 1 + (x - 1) * 4 / 8

rating_plot <- function(metric) {
  resp <- responses[responses$metric == metric, ]
  summ <- data.frame(
    year          = evals$year,
    role          = evals$role,
    mean_9        = five_to_nine(evals[[metric]]),
    n             = evals$n_responses,
    response_rate = evals$response_rate
  )

  ggplot() +
    geom_violin(
      data = resp,
      aes(x = year, y = rating_9, group = interaction(year, role),
          fill = role, alpha = response_rate, weight = count),
      width = 1.4, scale = "width", colour = NA, bw = 0.6
    ) +
    geom_line(
      data = summ,
      aes(x = year, y = mean_9, group = role, color = role,
          alpha = response_rate),
      linewidth = 0.8
    ) +
    geom_point(
      data = summ,
      aes(x = year, y = mean_9, color = role, shape = role,
          alpha = response_rate, size = n)
    ) +
    geom_label(
      data = summ,
      aes(x = year, y = mean_9, color = role, label = paste0("n=", n)),
      vjust = -0.8, hjust = 0.5, size = 3.2, alpha = 1,
      fill = "white", label.size = 0.3, label.padding = unit(0.15, "lines"),
      label.r = unit(0.1, "lines"), fontface = "bold",
      show.legend = FALSE
    ) +
    scale_x_continuous(breaks = year_breaks) +
    scale_y_continuous(
      name = "UCLA (9-pt)",
      breaks = 1:9,
      sec.axis = sec_axis(
        transform = nine_to_five,
        name = "UC Davis (5-pt)",
        breaks = 1:5
      )
    ) +
    coord_cartesian(ylim = c(1, 9), clip = "off") +
    scale_fill_manual(values = role_colors, name = "Role",
                      guide = guide_legend(order = 1)) +
    scale_color_manual(values = role_colors, name = "Role",
                       guide = guide_legend(order = 1)) +
    scale_shape_discrete(name = "Role", guide = guide_legend(order = 1)) +
    scale_size_continuous(range = c(2.5, 5), name = "Respondents",
                          guide = guide_legend(order = 2)) +
    scale_alpha_continuous(
      range = c(0.25, 1), limits = c(0, 1),
      breaks = c(0.25, 0.5, 0.75, 1),
      labels = scales::percent,
      name = "Response rate",
      guide = guide_legend(order = 3, override.aes = list(size = 4))
    ) +
    labs(x = "Year") +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.box = "vertical",
      plot.margin = margin(t = 18, r = 8, b = 4, l = 4)
    )
}

response_rate_plot <- function() {
  ggplot(evals, aes(x = year, y = response_rate, color = role, shape = role)) +
    geom_line(aes(group = role), linewidth = 0.8) +
    geom_point(aes(size = n_responses)) +
    geom_text(aes(label = paste0("n=", n_responses)),
              vjust = -1.4, hjust = 0.5, size = 3, show.legend = FALSE) +
    scale_x_continuous(breaks = year_breaks) +
    scale_y_continuous(labels = scales::percent, breaks = seq(0, 1, 0.25)) +
    coord_cartesian(ylim = c(0, 1), clip = "off") +
    scale_size_continuous(range = c(2.5, 5), name = "Respondents",
                          guide = guide_legend(order = 2)) +
    scale_color_manual(values = role_colors, name = "Role",
                       guide = guide_legend(order = 1)) +
    scale_shape_discrete(name = "Role", guide = guide_legend(order = 1)) +
    labs(x = "Year", y = "Response rate") +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.box = "vertical",
      plot.margin = margin(t = 18, r = 8, b = 4, l = 4)
    )
}
```

::: {#fig-evals layout-ncol=2}

```{r}
#| label: fig-overall
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Overall rating. Left axis: UCLA 9-point (1 = Very Low … 9 = Very High). Right axis: UC Davis 5-point (1 = Poor … 5 = Excellent)."
rating_plot("overall_rating")
```

```{r}
#| label: fig-instructor
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Instructor effectiveness. Left axis: UCLA 9-point (1 = Very Low … 9 = Very High). Right axis: UC Davis 5-point (1 = Poor … 5 = Excellent)."
rating_plot("instructor_effectiveness")
```

```{r}
#| label: fig-organization
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Course was well-organized. Left axis: UCLA 9-point (1 = Very Low … 9 = Very High). Right axis: UC Davis 5-point (1 = Strongly Disagree … 5 = Strongly Agree)."
rating_plot("course_organization")
```

```{r}
#| label: fig-response-rate
#| echo: false
#| fig-width: 7
#| fig-height: 4
#| fig-cap: "Response rate (respondents ÷ enrolled). No error bars — this is a population proportion, not a sample mean."
response_rate_plot()
```

Teaching-evaluation trends over time. The three rating panels share a dual y-axis: the **left axis** is the UCLA TA 9-point Likert scale, the **right axis** is the UC Davis IOR 5-point scale, and the two are linearly aligned. UC Davis responses (originally on the 5-point scale) are stretched onto the 9-point axis so both sets of distributions sit in the same coordinate space — so e.g. a UC Davis rating of 4 plots at 7 on the left axis, which the right axis correctly reads as 4. **Violins show the kernel density of individual respondent ratings** (a measure of student-to-student spread), weighted by their count in the histogram from each summary. Lines and points show the mean trend; point size is proportional to the number of respondents (also labeled `n=...`), and **opacity is proportional to the response rate** (responses ÷ enrolled). The three rating items use different Likert anchors and aren't directly comparable across panels.

:::

## UC Davis (Instructor of Record)

### Epi 204

#### 2025

- [Epi 204 Evaluations Summary (2025)](files/evals/evals%20epi%20204%202025%20summary.pdf)

#### 2024

- [Epi 204 Evaluations Summary (2024)](files/evals/Evaluations%20epi%20204%202024%20summary.pdf)

#### 2023

- [Epi 204 Evaluations (Spring 2023)](files/evals/Epi%20204%20Evaluations%20Spring%202023.pdf)

## UCLA (Teaching Assistant)

### Winter 2017

- [Teaching Evaluation 1](files/evals/Morrison%20teaching%20eval%201.pdf)
- [Teaching Evaluation 2](files/evals/Morrison%20teaching%20eval%202.pdf)
